Simulation Study: Varying Effect Size (t noise)

### 2018-06-05 datasets/simulations/simulations-varyingeffectsize-chisq.Rmd
Add unimodal sims with chisq, t noise

In this set of simulations, we consider settings with both null and non-null
tests with varying distribution of effect sizes under the non-null (alternative)
setting. An informative covariate is included in the setting as described in
`simulations-informative-sine.Rmd`.

@@

## intermediary files we create below
spiky_file <- file.path(resdir, "varyinges-benchmark-spiky.rds")
flattop_file <- file.path(resdir, "varyinges-benchmark-flattop.rds")
skew_file <- file.path(resdir, "varyinges-benchmark-skew.rds")
bimodal_file <- file.path(resdir, "varyinges-benchmark-bimodal.rds")

@@

```{r parameters-shared}
m <- 20000                          # integer: number of hypothesis tests
pi0 <- pi0_sine(0.90)               # numeric: proportion of null hypotheses
tstat_dist <- rnorm_perturber(1/2)  # functional: sampling dist/noise for test stats
null_dist <- rnorm_2pvaluer(1/2)    # functional: dist to calc p-values
icovariate <- runif                 # functional: independent covariate
```

@@

```{r spiky-parameters}
tstat <- sampler_spiky       # functional: dist of alternative test stats
seed <- 778
```

@@

```{r flattop-parameters}
tstat <- sampler_flat_top       # functional: dist of alternative test stats
seed <- 980
```

@@

```{r skew-parameters}
tstat <- sampler_skew       # functional: dist of alternative test stats
seed <- 206
```

@@

```{r bimodal-parameters}
tstat <- sampler_bimodal       # functional: dist of alternative test stats
seed <- 913
```

>>>>

In this set of simulations, we consider settings with both null and non-null
tests with varying distribution of effect sizes under the non-null (alternative)
setting. An informative covariate is included in the setting as described in
`simulations-informative-sine.Rmd`. This set of simulations is similar to those
presented in `simulations-varyingeffectsize.Rmd`, however, Chi-Squared
distributed noise is used to perturb effects. Additionally, since the effect
must be non-negative (to be a valid value for the non-centrality parameter
of the a Chi-Squared distribution), the absolute value of all effect sizes
are used. Note that this modification still maintains a unimodal distribution
of the effect sizes for all settings except the "bimodal" case below.

@@

## intermediary files we create below
spiky_file <- file.path(resdir, "varyinges-chisq-benchmark-spiky.rds")
flattop_file <- file.path(resdir, "varyinges-chisq-benchmark-flattop.rds")
skew_file <- file.path(resdir, "varyinges-chisq-benchmark-skew.rds")
bimodal_file <- file.path(resdir, "varyinges-chisq-benchmark-bimodal.rds")

@@

```{r parameters-shared}
m <- 20000                          # integer: number of hypothesis tests
pi0 <- pi0_sine(0.90)               # numeric: proportion of null hypotheses
tstat_dist <- rchisq_perturber(4)   # functional: sampling dist/noise for test stats
null_dist <- rchisq_pvaluer(4)      # functional: dist to calc p-values
icovariate <- runif                 # functional: independent covariate
```

@@

```{r spiky-parameters}
tstat <- function(n) { abs(sampler_spiky(n)) } # functional: dist of alternative test stats
seed <- 778
```

@@

```{r flattop-parameters}
tstat <- function(n) { abs(sampler_flat_top(n)) }       # functional: dist of alternative test stats
seed <- 980
```

@@

```{r skew-parameters}
tstat <- function(n) { abs(sampler_skew(n)) }       # functional: dist of alternative test stats
seed <- 206
```

@@

```{r bimodal-parameters}
tstat <- function(n) { abs(sampler_bimodal(n)) }       # functional: dist of alternative test stats
seed <- 913
```

### 2018-06-05 datasets/simulations/simulations-varyingeffectsize-t.Rmd
Add unimodal sims with chisq, t noise

---
title: "Simulation Study: Varying Effect Size"
author: "Patrick Kimes"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
   html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
---

@@

In this set of simulations, we consider settings with both null and non-null
tests with varying distribution of effect sizes under the non-null (alternative)
setting. An informative covariate is included in the setting as described in
`simulations-informative-sine.Rmd`.

@@

## intermediary files we create below
spiky_file <- file.path(resdir, "varyinges-benchmark-spiky.rds")
flattop_file <- file.path(resdir, "varyinges-benchmark-flattop.rds")
skew_file <- file.path(resdir, "varyinges-benchmark-skew.rds")
bimodal_file <- file.path(resdir, "varyinges-benchmark-bimodal.rds")

@@

```{r parameters-shared}
m <- 20000                          # integer: number of hypothesis tests
pi0 <- pi0_sine(0.90)               # numeric: proportion of null hypotheses
tstat_dist <- rnorm_perturber(1/2)  # functional: sampling dist/noise for test stats
null_dist <- rnorm_2pvaluer(1/2)    # functional: dist to calc p-values
icovariate <- runif                 # functional: independent covariate
```

>>>>

---
title: "Simulation Study: Varying Effect Size (t noise)"
author: "Patrick Kimes"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
   html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
---

@@

In this set of simulations, we consider settings with both null and non-null
tests with varying distribution of effect sizes under the non-null (alternative)
setting. An informative covariate is included in the setting as described in
`simulations-informative-sine.Rmd`. This set of simulations is similar to those
presented in `simulations-varyingeffectsize.Rmd`, however, t-distributed noise
is used to perturb effects.

@@

## intermediary files we create below
spiky_file <- file.path(resdir, "varyinges-t-benchmark-spiky.rds")
flattop_file <- file.path(resdir, "varyinges-t-benchmark-flattop.rds")
skew_file <- file.path(resdir, "varyinges-t-benchmark-skew.rds")
bimodal_file <- file.path(resdir, "varyinges-t-benchmark-bimodal.rds")

@@

```{r parameters-shared}
m <- 20000                          # integer: number of hypothesis tests
pi0 <- pi0_sine(0.90)               # numeric: proportion of null hypotheses
tstat_dist <- rt_perturber(5)       # functional: sampling dist/noise for test stats
null_dist <- rt_2pvaluer(5)         # functional: dist to calc p-values
icovariate <- runif                 # functional: independent covariate
```
